Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/discussion.tex
discussion

@@

Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear on undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.

@@

\begin{figure}[h]
\centering
\includegraphics[width=3in]{posneg}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}

>>>>

% examples.
In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
due to the same word being used in a different context.
For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
better code generation with GCC at least.''}
This comment, \emph{``I'll study the generated code a bit more,''} is not technically contributing, but is classified as a useful comment, which may be because of the word \emph{generate} appears both documents.

@@

Another approach we tried is to perform a \emph{binary classification}.
This means we assume that there are no unclear or undetermined comments; only useful and useless.
For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.

@@

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{posneg}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}
